---
title: "Using the Senaps API from R with RSenaps"
author: "Bangyou Zheng"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(RSenaps)
```

# Introduction

`RSenaps` is an R package to manage communication with the [Senaps API](http://sensor-cloud.io). 

## Authentication management

Use of the Senaps API requires a user account. You can create one via [Senaps](http://sensor-cloud.io). 

The API accepts authentication with either an API key, or username/password. It it *STRONGLY RECOMMENDED* that you use an API key for authentication, *NOT* a username and password. 

Regardless of which you use, never store credentials in a script, or commit them to a version control repository.

The best way to manage your credentials is with an environment variable, through a `.Renviron` file. Create the `.Renviron` file in root of your directory with contents of the structure:

`SENAPS_APIKEY=putyourkeyhere`

(replace `putyourkeyhere` with your actual key from Senaps).

The key is then accessible in R with `Sys.getenv('SENAPS_APIKEY')`.


To set your API key with RSenaps, use `senaps_options()` function:

```{r}
senaps_options(apikey = Sys.getenv('SENAPS_APIKEY'))
```


# Sensor Data

## Accessing sensor observations


# Data Service

## Downloading data

## Uploading data

# Analytics Service

## Uploading a model